---
title: "WSMA ASSIGNMENT of Twitter data company verizon"
author: "Group"
date: "2 July 2017"
output:
  html_document: default
  pdf_document: default
---

Use Twitter data on 2017 on verizon to demonstrate text mining and visualization techniques including text cleanup, word cloud, frequent terms, topic modelling and sentiment analysis 
```{r setup, include=FALSE}
#Setup the environment

rm(list=ls())
library(SnowballC)
library(tm)
library(ggplot2)
library(RColorBrewer)
library(wordcloud)
library(topicmodels)
library(data.table)
library(stringi)
library(devtools)
library(sentiment)
library(dplyr)
library(rJava)
library(qdap)


```
##### read twitter data
```{r}
# Set directory and read data
getwd()

#verizon<-write.csv(tweetsc.df,file = "verizon.csv")
tweets.df <- read.csv("verizon.csv")
# Convert char date to correct date format
head(tweets.df)
tweets.df$created <- as.Date(tweets.df$created, format= "%Y-%m-%d")

head(tweets.df)
#View(tweets.df)
```
#####Cleaning the text data by removing links, tags and delimiters.   
#####Build a Corpus, and specify the location to be the character Vectors 
```{r}
# Remove character string between < >
tweets.df$text <- genX(tweets.df$text, " <", ">")

# Create document corpus with tweet text
myCorpus<- Corpus(VectorSource(tweets.df$text))
```
##### convert to Lowercase
```{r}
myCorpus <- tm_map(myCorpus, content_transformer(stri_trans_tolower))
```
##### Remove the links (URLs)
```{r}
removeURL <- function(x) gsub("http[^[:space:]]*", "", x)  
myCorpus <- tm_map(myCorpus, content_transformer(removeURL))
```
##### Remove anything except the english language and space
```{r}
removeNumPunct <- function(x) gsub("[^[:alpha:][:space:]]*", "", x)   
myCorpus <- tm_map(myCorpus, content_transformer(removeNumPunct))
myCorpus <- tm_map(myCorpus,removeNumbers)
```
##### Remove Stopwords
```{r}
myStopWords<- c((stopwords('english')),c("rt", "use", "used", "via", "amp","NHP","lol","VZWSupport","stw" ,"yday" ,"isdst","character"))
myCorpus<- tm_map(myCorpus,removeWords , myStopWords) 
```
##### Remove Single letter words
```{r}
removeSingle <- function(x) gsub(" . ", " ", x)   
myCorpus <- tm_map(myCorpus, content_transformer(removeSingle))
```
##### Remove Extra Whitespaces
```{r}
myCorpus<- tm_map(myCorpus, stripWhitespace) 
```
##### remove punctuation
```{r}
myCorpus <- tm_map(myCorpus, content_transformer(removeNumPunct))
```
##### remove number
```{r}
myCorpus <- tm_map(myCorpus,removeNumbers)
```

##### keep a copy of "myCorpus" for stem completion later
```{r}
myCorpusCopy<- myCorpus
```
##### Stem words in the corpus
```{r}
myCorpus<-tm_map(myCorpus, stemDocument)
writeLines(strwrap(myCorpus[[250]]$content,60))
```
##### Function to correct/complete the text after stemming
```{r}
stemCompletion2 <- function(x,dictionary) {
  x <- unlist(strsplit(as.character(x)," "))
  x <- x[x !=""]
  x <- stemCompletion(x, dictionary = dictionary)
  x <- paste(x, sep="", collapse=" ")
  PlainTextDocument(stripWhitespace(x))
}
```
##### Stem Complete and Display the same tweet above with the completed and corrected text.
```{r}
myCorpus <- lapply(myCorpus, stemCompletion2, dictionary=myCorpusCopy)
myCorpus <- Corpus(VectorSource(myCorpus))
writeLines(strwrap(myCorpus[[250]]$content, 60))
```
##### Correcting mis-splet words
```{r}
wordFreq <- function(corpus,word)
{
  results<- lapply(corpus,
                   function(x){ grep(as.character(x),pattern = paste0("\\<", word))})
  sum(unlist(results))
}
n.tenni<- wordFreq(myCorpusCopy, "wday")
n.tennis <- wordFreq(myCorpusCopy, "wed")
cat(n.tenni, n.tennis)
```
#####Used to replace words with the proper ones
```{r}
replaceWord <- function(corpus, oldword, newword)
{
  tm_map(corpus, content_transformer(gsub), pattern=oldword, replacement=newword)
  }
myCorpus<- replaceWord(myCorpus, "wday", "wed")

tdm<- TermDocumentMatrix(myCorpus, control= list(wordLengths= c(1, Inf)))
tdm
```
```{r}
idx <- which(dimnames(tdm)$Terms %in% c("us", "unlimited"))
as.matrix(tdm[idx,21:60])
```

##### Find the terms used most frequently
```{r}
(freq.terms <- findFreqTerms(tdm, lowfreq = 50))
```
```{r}
term.freq <- rowSums(as.matrix(tdm))
term.freq <- subset(term.freq, term.freq > 50)
df <- data.frame(term = names(term.freq), freq= term.freq)
```
##### plotting the graph of frequent terms
```{r}
ggplot(df, aes(reorder(term, freq),freq)) + theme_bw() + geom_bar(stat = "identity")  + coord_flip() +labs(list(title="Term Frequency Chart", x="Terms", y="Term Counts")) 
```
##### calculate the frequency of words and sort it by frequency and setting up the Wordcloud
```{r}
word.freq <-sort(rowSums(as.matrix(tdm)), decreasing= F)
pal<- brewer.pal(8, "Dark2")
wordcloud(words = names(word.freq), freq = word.freq, min.freq = 2, random.order = F, colors = pal, max.words = 100)
```
##### # Identify and plot word correlations. For example - quality
```{r}
library(qdap)
#WordCorr <- apply_as_df(myCorpus[1:500], word_cor, word = "love", r=.25)
#plot(WordCorr)
```
```{r}
#qheat(vect2df(WordCorr[[1]], "word", "cor"), values=TRUE, high="red",
#digits=2, order.by ="cor", plot = FALSE) + coord_flip()
# Messages with word - love
#df <- data.frame(text=sapply(myCorpus, `[[`, "content"), stringsAsFactors=FALSE)
#head(unique(df[grep("love", df$text), ]), n=10)
```
##### find association
```{r}
findAssocs(tdm, "network", 0.2)
```

```{r}
findAssocs(tdm, "service", 0.2)
```
##### Topic Modelling to identify latent/hidden topics using LDA technique
```{r}
dtm <- as.DocumentTermMatrix(tdm)

rowTotals <- apply(dtm , 1, sum)

NullDocs <- dtm[rowTotals==0, ]
dtm   <- dtm[rowTotals> 0, ]

if (length(NullDocs$dimnames$Docs) > 0) {
tweets.df <- tweets.df[-as.numeric(NullDocs$dimnames$Docs),]
}

lda <- LDA(dtm, k = 10) # find 5 topic
term <- terms(lda, 7) # first 7 terms of every topic
(term <- apply(term, MARGIN = 2, paste, collapse = ", "))
```
```{r}
topics<- topics(lda)
topics<- data.frame(date=(tweets.df$created), topic = topics)
qplot (date, ..count.., data=topics, geom ="density", fill= term[topic], position="stack")
```

```{r}
sentiments <- polarity(tweets.df$text)
sentiments <- data.frame(sentiments$all$polarity)

sentiments[["polarity"]] <- cut(sentiments[[ "sentiments.all.polarity"]], c(-5,0.0,5), labels = c("negative","positive"))

table(sentiments$polarity)
```
```{r}
sentiments$score<- 0
sentiments$score[sentiments$polarity == "positive"]<-1
sentiments$score[sentiments$polarity == "negative"]<- -1
sentiments$date <- as.IDate(tweets.df$created)
result <- aggregate(score ~ date, data = sentiments, sum)
plot(result, type = "l")
```
##### Stream Graph for sentiment by date
```{r}
Data<-data.frame(sentiments$polarity)
colnames(Data)[1] <- "polarity"
Data$Date <- tweets.df$created
Data$text <- NULL
Data$Count <- 1
graphdata <- aggregate(Count ~ polarity + as.character.Date(Date),data=Data,FUN=length)
colnames(graphdata)[2] <- "Date"
str(graphdata)
```


